Gender Dynamics in Financial Decision-Making: Unveiling the Money Illusion Effect in Brazil

### 2024-02-15 outputs/paper/paper.qmd
Fixed abstract issue

---
title: "Gender Dynamics in Financial Decision-Making: Unveiling the Money Illusion Effect in Brazil"
title-block-banner: true
abstract: "Money illusion is a cognitive bias where individuals focus on nominal rather than real values, a concept initially highlighted by Shafir, Diamond, and Tversky (1997). In this study, we replicated four scenarios from their research within the Brazilian context, involving 372 participants making financial decisions impacted by money illusion in contexts of earnings and transactions. Through our analysis, we found that decision-making was significantly influenced by the framing of information, with notable differences in rationality between genders. Our findings highlight that the effects of money illusion may also vary by gender, showcasing distinct patterns of financial behavior between males and females."
thanks: "Code and data supporting this analysis are available at https://github.com/TEJMaster/Replication-For-Money-Illusion.git Replication on Social Science Reproduction platform available at: https://www.socialsciencereproduction.org/reproductions/1671/published/index"
author: "Terry Tu, Jingyi Shen, Yaning Jin "
date: today
date-format: long
format: pdf
toc: true
toc-depth: 1
number-sections: true
bibliography: references.bib
link-citations: true
editor: 
  markdown: 
    wrap: sentence
---

>>>>

---
title: "Gender Dynamics in Financial Decision-Making: Unveiling the Money Illusion Effect in Brazil"
title-block-banner: true
abstract: "Money illusion is a cognitive bias where individuals focus on nominal rather than real values, a concept initially highlighted by Shafir, Diamond, and Tversky (1997). In this study, we replicated four scenarios from their research within the Brazilian context, involving 372 participants, to explore the impact of gender on financial decision-making under the influence of money illusion. Our analysis revealed significant gender differences in decision-making, with males and females exhibiting distinct patterns of financial behavior when information was framed differently. These findings underscore the importance of considering gender in economic policies and financial education programs, as the effects of money illusion may vary between males and females, influencing their economic decisions and behaviors."
thanks: "Code and data supporting this analysis are available at https://github.com/TEJMaster/Replication-For-Money-Illusion.git Replication on Social Science Reproduction platform available at: https://www.socialsciencereproduction.org/reproductions/1671/published/index"
author: "Terry Tu, Jingyi Shen, Yaning Jin "
date: today
date-format: long
format: pdf
toc: true
toc-depth: 1
number-sections: true
bibliography: references.bib
link-citations: true
editor: 
  markdown: 
    wrap: sentence
---
